---
title: "Coping with Adversity: Logistics Mixed Effects Models"
date: "February 12, 2018"
output:
  pdf_document: default
  html_notebook: default
---

```{r}
# Load packages
library(lme4)
require(lme4)

# Load data for linear analysis (centered and scaled already)
MDS_data <- read.table("/Users/drewjmclaughlin/Desktop/Multi-ACs-Study-Data.txt",
                       header=TRUE)
```

```{r}
# Full logistics mixed model with interactions
MDSInt.lmer <- glmer(CorrectIncorrect ~ Condition*PPVTScale + Condition*RhythmScale + 
                     Condition*StroopScale + Condition*WARRMScale + (1|Subject), 
                   data=MDS_data, family="binomial")
```
#
Stroop's interaction with Condition does not significantly improve model fit:  

```{r}
# Remove Stroop*Condition interaction and compare models with ANOVA
MDSIntNoStroopCond.lmer <- glmer(CorrectIncorrect ~ Condition*PPVTScale + 
                                   Condition*RhythmScale + StroopScale + 
                                   Condition*WARRMScale + (1|Subject), data=MDS_data, 
                                 family="binomial")
anova(MDSIntNoStroopCond.lmer, MDSInt.lmer)
```
#
Stroop does not significantly improve model fit (Stroop is excluded from this point on):  

```{r}
# Remove Stroop entirely and compare models with ANOVA
MDSIntNoStroop.lmer <- glmer(CorrectIncorrect ~ Condition*PPVTScale + Condition*RhythmScale 
                             + Condition*WARRMScale + (1|Subject), data=MDS_data, 
                           family="binomial")
anova(MDSIntNoStroopCond.lmer, MDSIntNoStroop.lmer)
```
#
PPVT's interaction with Condition does not significantly improve model fit:  

```{r}
# Remove PPVT*Condition interaction and compare models with ANOVA
MDSIntNoPPVTCond.lmer <- glmer(CorrectIncorrect ~ PPVTScale + Condition*RhythmScale +
                               Condition*WARRMScale + (1|Subject), data=MDS_data, 
                             family="binomial")
anova(MDSIntNoStroop.lmer, MDSIntNoPPVTCond.lmer)
```
#
PPVT **does** significantly improve model fit:  

```{r}
# Remove PPVT entirely and compare with ANOVA
MDSIntNoPPVT.lmer <- glmer(CorrectIncorrect ~ Condition*RhythmScale + Condition*WARRMScale +
                           (1|Subject), data=MDS_data, family="binomial")
anova(MDSIntNoPPVT.lmer, MDSIntNoPPVTCond.lmer)
```
#
Rhythm's interaction with Condition **does** significantly improve model fit:  

```{r}
# Remove Rhythm*Condition interaction and compare models with ANOVA
MDSIntNoRhythmCond.lmer <- glmer(CorrectIncorrect ~ Condition*PPVTScale + RhythmScale + 
                                   Condition*WARRMScale + (1|Subject), data=MDS_data, 
                                 family="binomial")
anova(MDSIntNoStroop.lmer, MDSIntNoRhythmCond.lmer)
```
#
Rhythm does not significantly improve model fit:  

```{r}
# Remove Rhythm entirely and compare models with ANOVA
MDSIntNoRhythm.lmer <- glmer(CorrectIncorrect ~ Condition*PPVTScale + Condition*WARRMScale +
                               (1|Subject), data=MDS_data, family="binomial")
anova(MDSIntNoRhythm.lmer, MDSIntNoRhythmCond.lmer)
```
#
WARRM's interaction with Condition **does** significantly improve model fit:  

```{r}
# Remove WARRM*Condition interaction and compare models with ANOVA
MDSIntNoWARRMCond.lmer <- glmer(CorrectIncorrect ~ Condition*PPVTScale + 
                                  Condition*RhythmScale + WARRMScale + (1|Subject), 
                                data=MDS_data, family="binomial")
anova(MDSIntNoStroop.lmer, MDSIntNoWARRMCond.lmer)
```
#
WARRM **does** significantly improve model fit:  

```{r}
# Remove WARRM entirely and compare models with ANOVA
MDSIntNoWARRM.lmer <- glmer(CorrectIncorrect ~ Condition*PPVTScale + Condition*RhythmScale +
                              (1|Subject), data=MDS_data, family="binomial")
anova(MDSIntNoWARRM.lmer, MDSIntNoWARRMCond.lmer)
```
#
### Model of best fit (NE intercept)

```{r}
MDS.lmerBestFit <- glmer(CorrectIncorrect ~ PPVTScale + RhythmScale*Condition + 
                           WARRMScale*Condition + WARRMScale + (1|Subject), 
                         data=MDS_data, family="binomial")
summary(MDS.lmerBestFit)
anova(MDS.lmerBestFit)
```
#
### Model of best fit (NI intercept)

```{r}
# Add new column to data frame that uses dummy coding
library(dplyr)
MDS_data$Cond.dummy <- recode_factor(MDS_data$Condition, "NaInfo" = "NaInfo", "NNEner" = 
                                       "NNEner","NaEner" = "NaEner", "NNQuiet" = "NNQuiet")

# Rerun model using new column
MDS.lmerBestFit <- glmer(CorrectIncorrect ~ PPVTScale + RhythmScale*Cond.dummy + 
                           WARRMScale*Cond.dummy + WARRMScale + (1|Subject), 
                         data=MDS_data, family="binomial")
summary(MDS.lmerBestFit)
```
#
### Model of best fit (NNQ intercept)

```{r}
# Add new column to data frame that uses dummy coding
library(dplyr)
MDS_data$Cond.dummy <- recode_factor(MDS_data$Condition, "NNQuiet" = "NNQuiet", "NaInfo" = 
                                       "NaInfo", "NNEner" = "NNEner", "NaEner" = "NaEner")

# Rerun model using new column
MDS.lmerBestFit <- glmer(CorrectIncorrect ~ PPVTScale + RhythmScale*Cond.dummy + 
                           WARRMScale*Cond.dummy + WARRMScale + (1|Subject), 
                         data=MDS_data, family="binomial")
summary(MDS.lmerBestFit)
```
#
### Model of best fit (NNE intercept)

```{r}
# Add new column to data frame that uses dummy coding
library(dplyr)
MDS_data$Cond.dummy <- recode_factor(MDS_data$Condition, "NNEner" = "NNEner", "NNQuiet" = 
                                       "NNQuiet", "NaInfo" = "NaInfo", "NaEner" = "NaEner")

# Rerun model using new column
MDS.lmerBestFit <- glmer(CorrectIncorrect ~ PPVTScale + RhythmScale*Cond.dummy + 
                           WARRMScale*Cond.dummy + WARRMScale + (1|Subject), 
                         data=MDS_data, family="binomial")
summary(MDS.lmerBestFit)
```